Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2017-04-10 apj.tex
new cor matrix

\documentclass{aastex61}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
\usepackage{graphicx}				% Use pdf, png, jpg, or epsÂ§ with pdflatex; use eps in DVI mode
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{lineno}
\usepackage{color}
\defcitealias{1999PASP..111...63F}{F99}
\linenumbers

@@

\author{     G.~Aldering}
\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, ?out???½
    1 Cyclotron Road, Berkeley, CA, 94720}

@@

To constrain the degrees of freedom and degeneracies inherent in the model we impose that
each of the vectors $k_0+1/N$ and $k_1+1/N$,  where $N$ is the number of objects in our sample, are element-wise $\ge 0$ and sum to one, i.e.\
these vectors are simplexes.
These
conditions break the 
degeneracies  $\gamma ^0\rightarrow a\gamma^0$, $k_0 \rightarrow a^{-1}k_0$ and $\gamma^1 \rightarrow a\gamma^1$, $k_1 \rightarrow a^{-1}k_1$
up to a $\pm$ sign.
Furthermore we impose
\begin{equation}
\langle \Delta \rangle=0, \langle k_0 \rangle=0, \langle k_1 \rangle=0, \gamma^0_U > 0, \gamma^1_U < 0.
\end{equation}
The first two conditions specify the definition of zero color relative to which the color excess is measured:
in a linear model this value is arbitrary.
The latter two exclude degenerate posterior space
associated
with the $\pm$ sign, i.e.\ simultaneous sign flips of
$\gamma^0$--$k_0$ and $\gamma^1$--$k_1$
(when running our fits, $k_0$ and $k_1$ are set to
identical initial conditions, so the difference in the signs of $\gamma^0_U$ and $\gamma^1_U$ distinguishes the two.)
As  $\gamma^0$--$k_0$ and $\gamma^1$--$k_1$ are degenerate with
each other,
the different initial and boundary conditions for $\gamma^0_U$ and $\gamma^1_U$ break the degeneracy of our mixture model;
otherwise identical initial conditions for $\gamma^0$, $\gamma^1$ produce indistinguishable posteriors
with relatively broad credible intervals and lower maximum likelihood.

@@

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^0}(B-V)$ are given in the matrix
\begin{multline}
Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V)) =\\
\begin{pmatrix}
\begin{array}{rrrrrr}
1.00 & 0.00 & -0.06 & -0.05 & 0.11 & 0.01 \\
0.00 & 1.00 & 0.10 & -0.26 & -0.07 & -0.01 \\
-0.06 & 0.10 & 1.00 & -0.14 & -0.17 & -0.03 \\
-0.05 & -0.26 & -0.14 & 1.00 & 0.03 & 0.03 \\
0.11 & -0.07 & -0.17 & 0.03 & 1.00 & 0.05 \\
0.01 & -0.01 & -0.03 & 0.03 & 0.05 & 1.00
\end{array}
\end{pmatrix}.
\end{multline}

@@

To constrain the new degrees of freedom and degeneracies inherent in the model we impose additional constraints.  We first
require that
$D+1/N$ be a simplex to break the 
degeneracy  $\delta \rightarrow a\delta$, $D \rightarrow a^{-1}D$.
Furthermore we impose
\begin{equation}
\langle D\rangle=0,\,  \delta \cdot \gamma^0=0,\, \delta \cdot \gamma^1=0.
\end{equation}
The first of these constraints specifies the definition of zero color.   The latter two confine possible magnitude
variations to be those that cannot be attributed to 
the $\gamma k$ terms (i.e.\ dust); this condition breaks the degeneracies between $\delta D$  
and $\gamma k$. 
Unlike for the $\gamma$'s, there is no condition on the sign of $\delta_U$,
so that the posterior has degenerate solutions with sign flips of $\delta$ and $D$.
\color{blue}
We apply the condition $\delta_I>0$ to break this degeneracy,
and assume a flat prior for the three linear components of the subspace perpendicular to the $\gamma$ plane.
\color{black}
In the running of the Monte Carlo fit, the initial conditions for
$\gamma^0$ and $\gamma^1$ were set to be in the neighborhood of the best fit of \S\ref{model:sec}
to maintain their correspondence between the two models.

@@

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta I}=\delta_I D$ are given in the matrix.
\begin{multline}
Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V),  A_{\delta I}) =\\
\begin{pmatrix}
\begin{array}{rrrrrrr}
1.00 & 0.00 & -0.07 & -0.04 & 0.11 & 0.01 & -0.06 \\
0.00 & 1.00 & 0.10 & -0.26 & -0.07 & -0.02 & -0.02 \\
-0.07 & 0.10 & 1.00 & -0.14 & -0.17 & -0.04 & 0.04 \\
-0.04 & -0.26 & -0.14 & 1.00 & 0.03 & 0.03 & -0.07 \\
0.11 & -0.07 & -0.17 & 0.03 & 1.00 & 0.05 & 0.06 \\
0.01 & -0.02 & -0.04 & 0.03 & 0.05 & 1.00 & 0.01 \\
-0.06 & -0.02 & 0.04 & -0.07 & 0.06 & 0.01 & 1.00
\end{array}
\end{pmatrix}.
\end{multline}
The correlation coefficients between the ``intrinsic'' and ``extrinsic'' parameters are $0.06$ and $0.01$.
This has two important implications:
First, while in principle a single physical color effect can affect both intrinsic and extrinsic parameters, from the correlations
there is no evidence
that this occurs.
Second, the intrinsic term is not a second-order extrinsic correction.

>>>>

\documentclass{aastex61}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{lineno}
\usepackage{color}
\defcitealias{1999PASP..111...63F}{F99}
\linenumbers

@@

\author{     G.~Aldering}
\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
    1 Cyclotron Road, Berkeley, CA, 94720}

@@

To constrain the degrees of freedom and degeneracies inherent in the model we
\color{orange}
implement
\color{black}
each of the vectors $k_0+1/N$ and $k_1+1/N$,  where $N$ is the number of objects in our sample, are element-wise $\ge 0$ and sum to one, i.e.\
these vectors are simplexes.
These
conditions break the 
degeneracies  $\gamma ^0\rightarrow a\gamma^0$, $k_0 \rightarrow a^{-1}k_0$ and $\gamma^1 \rightarrow a\gamma^1$, $k_1 \rightarrow a^{-1}k_1$
up to a $\pm$ sign.
Furthermore we impose
\begin{equation}
\langle \Delta \rangle=0, \langle k_0 \rangle=0, \langle k_1 \rangle=0, \gamma^0_U > 0, \gamma^1_U < 0.
\end{equation}
The first two conditions specify the definition of zero color relative to which the color excess is measured:
in a linear model this value is arbitrary.
The latter two exclude degenerate posterior space
associated
with the $\pm$ sign, i.e.\ simultaneous sign flips of
$\gamma^0$--$k_0$ and $\gamma^1$--$k_1$
(when running our fits, $k_0$ and $k_1$ are set to
identical initial conditions, so the difference in the signs of $\gamma^0_U$ and $\gamma^1_U$ distinguishes the two.)
As  $\gamma^0$--$k_0$ and $\gamma^1$--$k_1$ are degenerate with
each other,
the different initial and boundary conditions for $\gamma^0_U$ and $\gamma^1_U$ break the degeneracy of our mixture model;
otherwise identical initial conditions for $\gamma^0$, $\gamma^1$ produce indistinguishable posteriors
with relatively broad credible intervals and lower maximum likelihood.

@@

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^0}(B-V)$ are given in the matrix
\color{orange}
\begin{multline}
Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V)) =\\
\begin{pmatrix}
\begin{array}{rrrrrr}
1.00 & 0.00^{+0.06}_{-0.06} & -0.07^{+0.07}_{-0.06} & -0.04^{+0.06}_{-0.06} & 0.10^{+0.07}_{-0.07} & -0.00^{+0.08}_{-0.07} \\
0.00^{+0.06}_{-0.06} & 1.00 & 0.10^{+0.03}_{-0.03} & -0.26^{+0.03}_{-0.03} & -0.07^{+0.06}_{-0.06} & -0.01^{+0.08}_{-0.08} \\
-0.07^{+0.07}_{-0.06} & 0.10^{+0.03}_{-0.03} & 1.00 & -0.14^{+0.04}_{-0.03} & -0.17^{+0.05}_{-0.05} & -0.04^{+0.08}_{-0.07} \\
-0.04^{+0.06}_{-0.06} & -0.26^{+0.03}_{-0.03} & -0.14^{+0.04}_{-0.03} & 1.00 & 0.03^{+0.05}_{-0.06} & 0.03^{+0.08}_{-0.08} \\
0.10^{+0.07}_{-0.07} & -0.07^{+0.06}_{-0.06} & -0.17^{+0.05}_{-0.05} & 0.03^{+0.05}_{-0.06} & 1.00 & 0.06^{+0.08}_{-0.08} \\
-0.00^{+0.08}_{-0.07} & -0.01^{+0.08}_{-0.08} & -0.04^{+0.08}_{-0.07} & 0.03^{+0.08}_{-0.08} & 0.06^{+0.08}_{-0.08} & 1.00 \\
\end{array}
\end{pmatrix}.
\end{multline}
\color{black}

@@

To constrain the new degrees of freedom and degeneracies inherent in the model we impose additional constraints.  We first
\color{orange}
implement
\color{black}
$D+1/N$ as a simplex to
\color{orange}
help
\color{black}
break the 
degeneracy  $\delta \rightarrow a\delta$, $D \rightarrow a^{-1}D$.
Furthermore we impose
\begin{equation}
\langle D\rangle=0,\,  \delta \cdot \gamma^0=0,\, \delta \cdot \gamma^1=0.
\end{equation}
The first of these constraints specifies the definition of zero color.   The latter two confine possible magnitude
variations to be those that cannot be attributed to 
the $\gamma k$ terms (i.e.\ dust); this condition breaks the degeneracies between $\delta D$  
and $\gamma k$. 
Unlike for the $\gamma$'s, there is no condition on the sign of $\delta_U$,
so that the posterior has degenerate solutions with sign flips of $\delta$ and $D$.
\color{blue}
We apply the condition $\delta_I>0$ to break this degeneracy,
and assume a flat prior for the three linear components of the subspace perpendicular to the $\gamma$ plane.
\color{black}
In the running of the Monte Carlo fit, the initial conditions for
$\gamma^0$ and $\gamma^1$ were set to be in the neighborhood of the best fit of \S\ref{model:sec}
to maintain their correspondence between the two models.

@@

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta I}=\delta_I D$ are given in the matrix
\color{orange}
\begin{multline}
Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V),  A_{\delta I}) =\\
\begin{pmatrix}
\begin{array}{rrrrrrr}
1.00 & 0.00^{+0.06}_{-0.06} & -0.07^{+0.06}_{-0.07} & -0.04^{+0.06}_{-0.06} & 0.11^{+0.07}_{-0.07} & -0.00^{+0.07}_{-0.07} & -0.06^{+0.07}_{-0.06} \\
0.00^{+0.06}_{-0.06} & 1.00 & 0.11^{+0.03}_{-0.04} & -0.26^{+0.03}_{-0.03} & -0.07^{+0.06}_{-0.06} & -0.01^{+0.08}_{-0.08} & -0.01^{+0.08}_{-0.08} \\
-0.07^{+0.06}_{-0.07} & 0.11^{+0.03}_{-0.04} & 1.00 & -0.14^{+0.04}_{-0.03} & -0.17^{+0.05}_{-0.05} & -0.05^{+0.08}_{-0.07} & 0.04^{+0.07}_{-0.07} \\
-0.04^{+0.06}_{-0.06} & -0.26^{+0.03}_{-0.03} & -0.14^{+0.04}_{-0.03} & 1.00 & 0.03^{+0.06}_{-0.06} & 0.04^{+0.07}_{-0.08} & -0.08^{+0.10}_{-0.09} \\
0.11^{+0.07}_{-0.07} & -0.07^{+0.06}_{-0.06} & -0.17^{+0.05}_{-0.05} & 0.03^{+0.06}_{-0.06} & 1.00 & 0.06^{+0.08}_{-0.07} & 0.06^{+0.08}_{-0.07} \\
-0.00^{+0.07}_{-0.07} & -0.01^{+0.08}_{-0.08} & -0.05^{+0.08}_{-0.07} & 0.04^{+0.07}_{-0.08} & 0.06^{+0.08}_{-0.07} & 1.00 & 0.01^{+0.08}_{-0.07} \\
-0.06^{+0.07}_{-0.06} & -0.01^{+0.08}_{-0.08} & 0.04^{+0.07}_{-0.07} & -0.08^{+0.10}_{-0.09} & 0.06^{+0.08}_{-0.07} & 0.01^{+0.08}_{-0.07} & 1.00 \\
\end{array}
\end{pmatrix}.
\end{multline}
\color{black}
The correlation coefficients between the ``intrinsic'' and ``extrinsic'' parameters are $0.06$ and $0.01$.
This has two important implications:
First, while in principle a single physical color effect can affect both intrinsic and extrinsic parameters, from the correlations
there is no evidence
that this occurs.
Second, the intrinsic term is not a second-order extrinsic correction.
